Resurgence of the Airy function

### 2022-05-13 airy-resurgence.tex
Higher Airy scratch work
Improve coefficient calculation tools
Pull out falling factorials
Big thanks to Peter Taylor from MathOverflow.

\usepackage{url}
\usepackage[hmargin=1.5in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage[svgnames]{xcolor} %% for revisions
\usepackage{xparse} %% for squiggly underlines

@@

@@

\left[ z^{n-1} \big[ \big({-}\tfrac{\partial}{\partial z}\big)^{n-1} - 1 \big] - c_{n-2} z^{n-2} \big({-}\tfrac{\partial}{\partial z}\big)^{n-2} - \ldots - c_2 z \big({-}\tfrac{\partial}{\partial z}\big)^2 - c_1 z \big({-}\tfrac{\partial}{\partial z}\big) - c_0 \right] \varphi = 0,

@@

\left[ \big[ \big({-}\tfrac{\partial}{\partial z}\big)^{n-1} - 1 \big] - c_{n-2} z^{-1} \big({-}\tfrac{\partial}{\partial z}\big)^{n-2} - \ldots - c_2 z^{3-n} \big({-}\tfrac{\partial}{\partial z}\big)^2 - c_1 z^{2-n} \big({-}\tfrac{\partial}{\partial z}\big) - c_0 z^{1-n} \right] \varphi = 0,

@@

>>>>

\usepackage{url}
\usepackage[hmargin=1.5in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{eqnarray}
\usepackage{graphicx}
\usepackage[svgnames]{xcolor} %% for revisions
\usepackage{xparse} %% for squiggly underlines

@@

\color{DarkCyan}

@@

\left[ z^{n-1} \big[ \big({-}\tfrac{\partial}{\partial z}\big)^{n-1} - 1 \big] - c_n^{(1)} z^{n-2} \big({-}\tfrac{\partial}{\partial z}\big)^{n-2} - c_n^{(2)} z^{n-3} \big({-}\tfrac{\partial}{\partial z}\big)^{n-3} - \ldots - c_n^{(n-2)} z \big({-}\tfrac{\partial}{\partial z}\big) - c_n^{(n-1)} \right] \varphi = 0,

@@

\left[ \big[ \big({-}\tfrac{\partial}{\partial z}\big)^{n-1} - 1 \big] - c_n^{(1)} z^{-1} \big({-}\tfrac{\partial}{\partial z}\big)^{n-2} - c_n^{(2)} z^{-2} \big({-}\tfrac{\partial}{\partial z}\big)^{n-3} - \ldots - c_n^{(n-2)} z^{-(n-2)} \big({-}\tfrac{\partial}{\partial z}\big) - c_n^{(n-1)} z^{-(n-1)} \right] \varphi = 0.

@@

The coefficients are straightforward to calculate, but their pattern is hard to describe. Peter Taylor suggests writing
\[ c_n^{(k)} = (n+1)^{\underline{k+2}}\;R^{(k)} / n^k, \]
for $k > 1$, where the underlined power denotes the falling factorial. Then we get
\begin{equationarray*}{*{11}{c}}
R^{(2)} & = & \tfrac{1}{24} \\
R^{(3)} & = & \tfrac{1}{48} n \\
R^{(4)} & = & \tfrac{73}{5760} n^2 & + & \tfrac{1}{1152} n & - & \tfrac{1}{2880} \\
R^{(5)} & = & \tfrac{11}{1280} n^{3} & + & \tfrac{1}{768} n^{2} & - & \tfrac{1}{1920} n \\
R^{(6)} & = & \tfrac{3625}{580608} n^{4} & + & \tfrac{61}{41472} n^{3} & - & \tfrac{181}{322560} n^{2} & - & \tfrac{1}{41472} n & + & \tfrac{1}{181440} \end{equationarray*}
Searching for 580608 in the OEIS reveals that the leading coefficients are ``fractions appearing in a generalization of Carleman's inequality,'' listed in the OEIS as {\tt A249276} and {\tt A249277}.
\paragraph{Old scratch work}
For now, we can at least say with confidence that
c_3^{(1)} & = 1 & c_{n+1}^{(1)} & = \frac{n}{n-1}\,c_{n}^{(1)} & c_n^{(1)} & = \frac{1}{n} \left(\begin{matrix} n \\ 2 \end{matrix}\right)
and
\[ c_n^{(2)} = \frac{1}{n^2} \left(\begin{matrix} n+1 \\ 4 \end{matrix}\right) \]
and
c_n^{(3)} & = \frac{5}{2} \cdot \frac{1}{n^2} \left(\begin{matrix} n+1 \\ 5 \end{matrix}\right) \\
c_4^{(3)} & = \frac{1}{n^3} \left(\begin{matrix} n+1 \\ 4 \end{matrix}\right) (2n-5)(n-2) = \frac{3 \cdot 2}{n^3} \left(\begin{matrix} n+1 \\ 4 \end{matrix}\right) = \frac{1 \cdot 1}{(n-1)^2} \frac{(n+2)(n+1)n}{4!} \\
c_5^{(3)} & = \frac{1}{n^3} \left(\begin{matrix} n+1 \\ 4 \end{matrix}\right) (2n-5)(n-3) = \frac{5 \cdot 2}{n^3} \left(\begin{matrix} n+1 \\ 4 \end{matrix}\right) = \frac{3 \cdot 1}{(n-1)^2} \frac{(n+2)(n+1)n}{4!} \sim \frac{3}{1} \cdot \frac{6}{3} \\
c_6^{(3)} & = \frac{1}{n^3} \left(\begin{matrix} n+1 \\ 4 \end{matrix}\right) (2n-7)(n-3) = \frac{5 \cdot 3}{n^3} \left(\begin{matrix} n+2 \\ 4 \end{matrix}\right) = \frac{3 \cdot 2}{(n-1)^2} \frac{(n+2)(n+1)n}{4!} \sim \frac{2}{1} \cdot \frac{7}{4} \\
c_7^{(3)} & = \frac{1}{n^3} \left(\begin{matrix} n+1 \\ 4 \end{matrix}\right) (2n-7)(n-4) = \frac{7 \cdot 3}{n^3} \left(\begin{matrix} n+1 \\ 4 \end{matrix}\right) \sim \frac{5}{3} \cdot \frac{8}{5} \\
c_8^{(3)} & = \frac{1}{n^3} \left(\begin{matrix} n+1 \\ 4 \end{matrix}\right) (2n-9)(n-4) = \frac{7 \cdot 4}{n^3} \left(\begin{matrix} n+1 \\ 4 \end{matrix}\right) \sim \frac{3}{2} \cdot \frac{9}{6} \\
c_9^{(3)} & = \frac{1}{n^3} \left(\begin{matrix} n+1 \\ 4 \end{matrix}\right) (2n-9)(n-5) = \frac{9 \cdot 4}{n^3} \left(\begin{matrix} n+1 \\ 4 \end{matrix}\right) \sim \frac{7}{5} \cdot \frac{10}{7} \\
n^2 c_{n+1}^{(3)} & = \frac{n+3}{n-2} (n-1)^2 c_n^{(3)} \\
c_{n+1}^{(3)} & = \frac{n+3}{n-2} \left(\frac{n-1}{n}\right)^2 c_n^{(3)} \\
(n+1)^3 c_{n+1}^{(3)} & = \frac{n+3}{n-2} \left(\frac{n-1}{n}\right)^2 \left(\frac{n+1}{n}\right)^3 n^3 c_n^{(3)} = \frac{(n+3)(n+1)}{n(n-2)} \left(\frac{n^2 - 1}{n^2}\right)^2 \\
c_4^{(3)} & = \frac{5}{32}
and
c_n^{(n-1)} & = \frac{1}{n^{n-1}}\,(n-2)(2n-3)(3n-4) \cdots [(n-2)n - (n-1)] \\
& = \frac{1}{n} \left(1 - \frac{2}{n}\right) \left(2 - \frac{3}{n}\right) \left(3 - \frac{4}{n}\right) \cdots \left((n-2) - \frac{n-1}{n}\right).
